Recent Advances in Networking

### 2013-07-23 Compiled/intro/chapterlist.tex
Full compiled
fixes

\documentclass[a4paper,16pt]{article} 
\usepackage{a4wide,times,latexsym}
\usepackage[compact,tiny]{titlesec}
\usepackage{url}
\usepackage{times}
\usepackage{graphics}
\usepackage{color}
%\usepackage[pdftex]{hyperref}
\usepackage{multirow}

\pagestyle{empty}
\begin{document}

@@

\item \textbf{Collaboration Opportunities for Content Delivery and Network \\ Infrastructures} \\
Benjamin Frank, Ingmar Poese, Georgios Smaragdakis, Anja Feldmann, Bruce M. Maggs, Steve Uhlig, Vinay Aggarwal, and Fabian Schneider

>>>>

%\documentclass[a4paper,16pt]{article} 
%\usepackage{a4wide,times,latexsym}
%\usepackage[compact,tiny]{titlesec}
%\usepackage{url}
%\usepackage{times}
%\usepackage{graphics}
%\usepackage{color}
%%\usepackage[pdftex]{hyperref}
%\usepackage{multirow}

%\pagestyle{empty}
%\begin{document}

@@

\item \textbf{Collaboration Opportunities for Content Delivery and Network Infrastructures} \\
Benjamin Frank, Ingmar Poese, Georgios Smaragdakis, Anja Feldmann, Bruce M. Maggs, Steve Uhlig, Vinay Aggarwal, and Fabian Schneider
